---
title: "kNN Classifier"
author: "Vijay"
output: 
 html_document:
   theme: lumen
   highlight: haddock
   toc: true
   toc_float: true
   toc_depth: 3
---

### Objective
Universal bank is a young bank growing rapidly in terms of overall customer acquisition. The majority of these customers are liability customers (depositors) with varying sizes of relationship with the bank. The customer base of asset customers (borrowers) is quite small, and the bank is interested in expanding this base  rapidly in more loan business. In particular, it wants to explore ways of converting its liability customers to personal loan customers. A campaign that the bank ran last year for liability customers showed a healthy conversion rate of over 9% success. This has encouraged the retail marketing department to devise smarter campaigns with better target marketing. The goal is to use k-NN to predict whether a new customer will accept a loan offer. This will serve as the basis for the design of a new campaign.


### Libraries
Libraries which are called for data importing, manipulation, and algorithms used for model construction.
```{r,message=FALSE}
library(tidyverse)
library(caret)
library(class)
library(readr)
library(gmodels)
```


### Importing Data
Data is imported into Rstudio using readr library.
```{r,message=FALSE}
ub <- read_csv("UniversalBank.csv")
```
```{r}
# Structure of the data.
glimpse(ub)

# Converting the target varialbe to factor
class(ub$`Personal Loan`)
ub$`Personal Loan` <- as.factor(ub$`Personal Loan`)
```


Checking the missing values in the data.
```{r}
sapply(ub,anyNA)
```


### Data Pre-processing
Data is split into **train and test** partitions.
```{r}
set.seed(123)

# Creating the index of the samples
index <- createDataPartition(ub$Age,p=0.7,list=FALSE)

# Creating the training samples
train <- ub[index,]

# Creating the testing samples
test <- ub[-index,]

# Dimensions of the samples
dim(train)
dim(test)
```


**Scaling the data**


Since we are using the *distance metric* algorithm, there is need to generalize the data. Hence, *normalization* technique is used.
```{r}
# Excluding the "ID","AGE","PERSONAL LOAN" columns from the data
scaling <- preProcess(train[,-c(1,5,10)],method=c("center","scale"))
train.norm <- predict(scaling,train[,-c(1,5,10)])
train.norm$`Personal Loan` <- train$`Personal Loan`
test.norm <- predict(scaling,test[,-c(1,5,10)])
```


### Model Building
Building the *base model with default parameters* using 10 fold cross validation.
```{r}
# Performing the k-fold cross validation
myControl <- trainControl(method = "cv",number=10)

# Model with default parameters
model_default <- train(
  `Personal Loan`~.,
  data=train.norm,
  method="knn",
  trControl=myControl
  )
```


The maximum accuracy from the various values of K
```{r}
model_default$results[which.max(model_default$results$Accuracy),]
```


Building the *model with grid parameters* using 10 fold cross validation.
```{r}
# Grid Parameter K, ranging from 1 to 15
tuneGrid <- data.frame(k=seq(1,15,1))

# Model with tuneGrid
model_tune <- train(
  `Personal Loan`~.,
  data=train.norm,
  method="knn",
  trControl=myControl,
  tuneGrid=tuneGrid
)
```


The maximum accuracy from the various values of K
```{r}
model_tune$results[which.max(model_tune$results$Accuracy),]
```
```{r}
# Choosing the best hyper parameter
k_value <- model_tune$bestTune[[1]]
```


The *accuracy* of the best hyperparameter **k = `r model_tune$bestTune[[1]]`** is **`r max(model_tune$results$Accuracy)`**.


### Best Model
Using *class* package, knn model is built with best tuned parameters.
```{r}
best_model <- knn(train.norm[,-12],
                  test.norm,train.norm$`Personal Loan`,
                  k=k_value,prob = TRUE)
```


### Confusion Matrix
It is used to evaluate the performance of the model. 
```{r}
CrossTable(best_model,test$`Personal Loan`,prop.chisq = FALSE)
confusionMatrix(best_model,test$`Personal Loan`)
```

### Result
Predicting the new scenario whether the customer will accept a loan or not. If result is '1' then *loan accepted* else *loan rejected*
```{r}
(Result <- knn(train.norm[,-12],c(Age=40,Experience = 10, Income=84,Family=2,CCAvg=2,
                               Education=2,Mortgage=0,`Securities Account`=0,
                               `CD Account`=0,Online=1,CreditCard=1),train.norm$`Personal Loan`,
              k=k_value))
```
